Simulating Ultra High-Dimensional Multivariate Data Using the bigsimr R Package

### 2020-06-20 030-bigsimr-package.Rmd
dont evaluate rslurm jobs

```{r setup, eval = TRUE}
## bookdown::preview_chapter('030-bigsimr-package.Rmd')
library(bigsimr)
```

@@

```{r rvecRslurm, echo=TRUE, eval=FALSE}
library(rslurm)
## a single call of rvec
## had to edit rslurm/templates/submit_single_sh.txt
## source ~/.bashrc
## conda activate bigsimr
## conda env config vars list
sjob <- slurm_call(rvec, jobname = 'rvec',
                   list(n=1e6,
                        rho = rho,
                        margins = margins,
                        type = "spearman"),
                   submit = TRUE)

res <- readRDS(file.path('_rslurm_rvec', list.files('_rslurm_rvec', 'results')))
head(res, 3)
cleanup_files(sjob) ## careful this deletes output also
```

```{r rvecRslurmApply, echo=TRUE, eval=TRUE}
library(rslurm)
## a single call of rvec
## had to edit rslurm/templates/submit_single_sh.txt
## source ~/.bashrc
## conda activate bigsimr
## conda env config vars list
sjob <- slurm_call(rvec, jobname = 'rvec',
                   list(n=1e6,
                        rho = rho,
                        margins = margins,
                        type = "spearman"),
                   submit = TRUE)

res <- readRDS(file.path('_rslurm_rvec', list.files('_rslurm_rvec', 'results')))
head(res, 3)
cleanup_files(sjob) ## careful this deletes output also
```

>>>>

```{r setup, eval = TRUE}
## bookdown::preview_chapter('030-bigsimr-package.Rmd')
## bookdown::render_book('index.html')
library(bigsimr)
```

@@

```{r rvecRslurm, echo=TRUE, eval=FALSE}
library(rslurm)
## a single call of rvec
## had to edit rslurm/templates/submit_single_sh.txt
## source ~/.bashrc
## conda activate bigsimr
## conda env config vars list
sjob <- slurm_call(rvec, jobname = 'rvec',
                   list(n=1e6,
                        rho = rho,
                        margins = margins,
                        type = "spearman"),
                   submit = TRUE)
```

```{r rvecRslurmRes, echo=TRUE, eval=TRUE}
res <- readRDS(file.path('_rslurm_rvec', list.files('_rslurm_rvec', 'results')))
head(res, 3)
## cleanup_files(sjob) ## careful this deletes output also
```
